### 2017-02-15 paper/response.Rmd

# @seaaan's Review

1. Documentation: README

> The README is very good! It gives a helpful overview of everything in the package and is clearly written, with good examples. All of the code examples worked on my computer. You might consider breaking the "experimental" parts of the package into a separate README like you do with the vignettes.

- Agreed, but I would prefer to keep the README as a whole piece, so I think instead I will just link to the experimental vignette as in the README. This has been logged in [issue 39]() and fixed in commit

@@

> In the "Using visdat" vignette, it says "missing data represented by black", but it shows up as gray on my computer.

- Interesting, it should be showing up as black, as this is what the [code and README reflect]() (well, grey50). Does it still happen now?

> I don't know why, but in the plotly section, a vis_dat() (non-interactive) plot of df_test appears between the first two interactive plots. I can't explain it, hopefully it's just a weird quirk on my computer.

- I can't seem to replicate this, can you maybe take a screenshot of this?

@@

> There is a "future work and experimental features" section in the "Using visdat" vignette -- I suggest transferring that to the experimental vignette and just linking to it from the "Using visdat" vignette. Perhaps move the vis_guess() and the interactive plots to the experimental features vignette as well, since they seem to be evolving.

- Agreed, this has been done in commit ... , issue ...

> The plot in the experimental features vignette shows up small, I think you need to add knitr::opts_chunk$set(fig.width = 5, fig.height = 4) to the first chunk like you have in the other vignette.

- Agreed, this has been completed in this commit ..., issue...

@@

# Function documentation

> Did you mean to export guess_type()?

- Yes, as I thought that it might be a useful function for users, although I can't think of a good usecase outside of `vis_guess` right now. Perhaps it might be best for `guess_type` to be unexported?

@@

> This is a minor issue, but was so thoroughly drummed into me by CS professors that I have to mention it. In calls like if (sort_type == TRUE), the == TRUE is redundant, so it's equivalent to just write if (sort_type). Similarly, if (x == FALSE) is equivalent to if (!x). There are a number of these in the code for various functions.

# vis_dat()

> Maximum data frame size: the heatmaps stop working on my computer with very large data sets. E.g. library(nycflights13); vis_dat(flights) hangs for a minute or so and then displays an empty grid. It works with 10000 rows, but not 100000. Similar issue with many columns. Especially because this package is designed for people to get a sense of new data sets, where users may not have realized how big the data are, I think it makes sense to prevent this issue. Possibilities: (1) max_rows = 10000 parameter, which stops if nrow(data) > max_rows and gives a descriptive error message. Then the user can increase the maximum or subset their data frame. Might also need to consider max_cols because 10000 rows and 2 cols is very different from 10000 rows and 500 cols. (2) Downsample the non-missing rows somehow and indicate to the user where omissions were made. (3) ???

- This is an interesting one! It was brought to my attention [here](), by @MilesMcBain, but I couldn't replicate this issue. Similarly, I can actually display the nycflights data. So it seems that this is to do with the fact that computations power has a bit to do with it. I think that option 1 is the best case here, but option 2 actually gets a little bit difficult, because this leads to another issue of effectively downsampling a dataset whilst maintaining key characteristics. This could a problem, say, if I did perform down-sampling and then the user looked at the data with visdat and plotly, they might get a mis-represented sample. Likewise, if there is a very large proportion of missing data, this might be difficult to preserve exactly. Ways around this might include some very explicit warning messages, or perhaps even a note directly on the plot that the data have been downsampled.

@@

> vis_guess lacks some of the parameters that vis_dat has, but should have the same options (except maybe not sort_type?)

> Performance: Setting the locale once and then calling collectorGuess instead of guess_parser is about 33% faster on my computer. I think the savings is by avoiding repeatedly calling the locale function and avoiding repeatedly calling stopifnot (inside the readr code).

```
l <- readr::locale()

output[!nas] <- vapply(FUN = function(y) readr:::collectorGuess(y, locale_ = l),
                       X = x[!nas], FUN.VALUE = character(1))

> If you're interested in converting to C++ for speed, I played around a little bit with implementing a vectorized version for guess_parser in readr. It's about 20X faster. Basically, I wrote a wrapper around collectorGuess that operates on a vector instead of single elements. This is faster because it does the looping in C++ rather than repeatedly transitioning from R to C++ and because it does some initial code once per vector instead of once per element. It is currently written as a modification of readr because that was more convenient, but I imagine it is possible to implement in your package as well. Let me know if you want to discuss that, but I'm definitely not an expert. To get it up and running, clone readr and then put this in readr/src/collectorGuess.cpp:

```
std::string collectorGuess2(const std::string& input, LocaleInfo locale) {

@@

> If you provide vis_miss_ly, it makes sense to me to also provide vis_dat_ly, and possibly also vis_compare_ly and vis_guess_ly. An initial implementation could just be vis_dat(x) %>% ggplotly(), but then you have the API in place at least.

# Tests

> Cool use of vdiffr and generally good coverage. The tests don't all pass on my machine (they are mostly skipped), which I think is because I don't have the .svg reference files on my computer.

- I think that this is the default behaviour of `vdiffr`? It states [here](https://github.com/lionel-/vdiffr#running-tests) that "New cases for which you just wrote an expectation will be skipped. Failed tests will show as an error."

@@

> vis_dat's power lies in the fact that it's essentially a visual analogue to one's data, if imagined as a frame/spreadsheet. In order to enhance this, I would suggest that the charts, by default, "read" in the spirit of this analogy by going from top to bottom.

## Documentation: README

> I have made some minor changes to the wording in README and submitted them as a pull request here, most of which I think are self-explanatory.

- Thank you! Pull request was merged [here](https://github.com/njtierney/visdat/commit/868140da16fbfc9150d8359731f4e9eb3e817675)

@@

- Agreed, this was addressed in commit ....

> When running the first example from README, (vis_dat(airquality)), the user will get a warning re. depecation of dmap(). If this is not of consequence to the package's functionality, then you might consider adding it to the suppressed messages. If it's something most users supress locally, then you might suggest that somewhere in the README.

```
#> dmap() is deprecated. Please use the new colwise family in dplyr.
#> E.g., summarise_all(), mutate_all(), etc.
```

- Thank you for finding this, I have addressed this in issue ..., and close that [here]().

### 2017-05-10 README.Rmd
better describe the airquality dataset, #39, #40
Add both vignettes, addressing issue #39

- `vis_miss()` visualises just the missing data, and allows for missingness to be clustered and columns rearranged. `vis_miss()` is similar to `missing.pattern.plot` from the [`mi`](https://cran.r-project.org/web/packages/mi/index.html) package. Unfortunately `missing.pattern.plot` is no longer in the `mi` package (well, as of 14/02/2016).

There are also experimental which are described in more detail in the [vignette: "Experimental Features of visdat](http://www.njtierney.com/visdat/articles/experimental_features.html).

@@

Let's see what's inside the `airquality` dataset from base R.

>>>>

- `vis_miss()` visualises just the missing data, and allows for missingness to be clustered and columns rearranged. `vis_miss()` is similar to `missing.pattern.plot` from the [`mi`](https://cran.r-project.org/web/packages/mi/index.html) package. Unfortunately `missing.pattern.plot` is no longer in the `mi` package (as of 14/02/2016).

You can read more about visdat in the vignette, ["using visdat""](http://www.njtierney.com/visdat/articles/using_visdat.html).

There are also experimental which are described in more detail in the vignette ["Experimental Features of visdat](http://www.njtierney.com/visdat/articles/experimental_features.html).

@@

Let's see what's inside the `airquality` dataset from base R, which contains information about daily air quality measurements in New York from May to September 1973. More information about the dataset can be found with `?airquality`.
